%------------------------------------------------------------------------------
% CV of Dmitry Kabanov.
% Created using LaTeX package `moderncv`.
%------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------
% Font sizes: 10, 11, 12
% Paper: a4paper, letterpaper, a5paper, legalpaper, executivepaper, landscape
% Font: sans or roman
\documentclass[11pt,letterpaper,sans]{moderncv} 

\usepackage[utf8]{inputenc}

% CV theme: casual (default), classic, oldstyle, banking
\moderncvstyle{classic}
% CV color: blue (default), orange, green, red, purple, grey, black
\moderncvcolor{blue}

% Width of the left column.
\setlength{\hintscolumnwidth}{2.7cm}

% `Merriweather` is a modern screen-friendly font
\usepackage{merriweather}

\usepackage[scale=0.80]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

% Remove dots in the end of \cventry lines.
\usepackage{xpatch}
\xpatchcmd{\cventry}{.\strut}{\strut}{}{}

\makeatletter
\makeatother

%------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%------------------------------------------------------------------------------

\firstname{Dmitry} % Your first name
\familyname{Kabanov} % Your last name

% All information in this block is optional, comment out any lines you don't need
% \title{Curriculum Vitae}
\address{King Abdullah University of Science and Technology\\Thuwal, Saudi Arabia\\}{}
\mobile{(+966 54) 470 1193}
\email{dmitry.kabanov@kaust.edu.sa}
\social[github]{dmitry-kabanov}
% \photo[picture-height][frame-thickness]{photo}
% \photo[70pt][0.2pt]{photo} 

\newcommand{\authors}{D.~I.~Kabanov, A.~R.~Kasimov}

\newcommand\Colorhref[3][color1]{\href{#2}{\small\color{#1}#3}}

%------------------------------------------------------------------------------
\begin{document}

%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

% Print the CV title
\makecvtitle%

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

% Arguments not required can be left empty.
\cventry{2012--2018}{PhD in Applied Mathematics and Computational Science}{}{}{}{}
\cvline{}{King Abdullah University of Science and Technology (KAUST), Thuwal, Saudi Arabia}
\cvline{dissertation}{Numerical computation of linear stability of detonations}
\cvline{advisor}{Aslan Kasimov}
\cventry{2004--2010}{Diploma of Engineer-Physicist}{}{}{}{}
\cvline{}{National Research Nuclear University MEPhI, Moscow, Russia}
\cvline{thesis}{Computation of one-dimensional detonation wave structure for ideal gases with detailed kinetic mechanisms}
\cvline{advisor}{Vladimir Shargatov}

%------------------------------------------------------------------------------
% Research interests
%------------------------------------------------------------------------------

\section{Research interests}

\cvline{}{
    Computational science,
    numerical methods,
    uncertainty quantification,
    differential equations,
    fluid dynamics,
    dynamical systems,
    machine learning,
    high-performance computing
}

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Research, computer, and soft skills}

\cvitem{}{Numerical methods for differential equations, numerical linear algebra}
\cvitem{}{Partial differential equations, fluid dynamics, stability theory}
\cvitem{}{Advanced knowledge of Unix, Python, Matlab, Git, shell scripting}
\cvitem{}{Proficiency in C, C++, MPI, OpenMP, SQL}
\cvitem{}{Ability to write clean and efficient numerical codes}
\cvitem{}{Unit testing and reproducibility in scientific computing}
\cvitem{}{Fluent English and Russian (native speaker)}

%----------------------------------------------------------------------------------------
%	Publications SECTION
%----------------------------------------------------------------------------------------

\section{Publications}


\cvitem{1}{\authors. A minimal hyperbolic system for unstable shock waves. \textit{Communications in Nonlinear Science and Numerical Simulation} 70 (2019), \Colorhref{https://doi.org/10.1016/j.cnsns.2018.10.022}{doi:10.1016/j.cnsns.2018.10.022}.}
\cvitem{2}{\authors. Linear stability analysis of detonations via numerical computation and dynamic mode decomposition. \textit{Physics of Fluids} 30, 036103 (2018), \Colorhref{https://doi.org/10.1063/1.5020558}{doi:10.1063/1.5020558}.}
\cvitem{3}{\authors. Numerical computation of linear stability of detonations. \emph{Proceedings of the 26th International
  Colloquium on the Dynamics of Explosions and Reactive Systems, August 2017, Boston,
  USA.}}
\cvitem{4}{\authors.
  Direct numerical computation of detonation linear stability: An example of
  the Fickett's detonation analog. \textit{Proceedings of the 10th
  International Colloquium on Pulsed and Continuous Detonations}, 2016,
  Saint-Petersburg, Russia.}

\section{Conferences}
\cvitem{Nov 2017}{\authors. Numerical computation of linear instability of detonations. \emph{Talk at the 70th Annual Meeting of the American Physical Society Division of Fluid Dynamics, Denver, USA.}}
\cvitem{Nov 2016}{\authors. Direct numerical computation of linear stability of gaseous detonations. \emph{Talk at the 69th Annual Meeting of the American Physical Society Division of Fluid Dynamics, Portland, USA.}}
\cvitem{Aug 2015}{\authors. Linear stability analysis of detonation models
  by direct numerical computations. \emph{Work-in-progress poster at the 25th International Colloquium on the Dynamics of Explosions and Reactive Systems, Leeds, UK.}}
\cvitem{Oct 2014}{\authors. Direct numerical analysis of linear stability of detonations. \emph{Work-in-progress poster at the Zel'dovich Memorial, Moscow, Russia.}}


\section{Professional Societies}
\cventry{2014--present}{Member of the Society of Industrial and Applied
    Mathematics (SIAM)}{}{}{}{}
\cventry{2015--present}{Member of the Combustion Institute}{}{}{}{}


%----------------------------------------------------------------------------------------
% Classes
%----------------------------------------------------------------------------------------

\section{Courses taken during PhD studies in KAUST}
\cvitem{}{Applied partial differential equations}
\cvitem{}{Numerical linear algebra}
\cvitem{}{Mathematical fluid dynamics}
\cvitem{}{Numerical analysis for differential equations}
\cvitem{}{Linear and nonlinear optimization}
\cvitem{}{Asymptotic methods}
\cvitem{}{High-performance computing}
\cvitem{}{Finite-element methods}
\cvitem{}{Stability and bifurcation of dynamical systems}
\cvitem{}{Nonlinear waves}
\cvitem{}{Hydrodynamic stability}
\cvitem{}{Special topics in numerical integration}



%----------------------------------------------------------------------------------------
%	References SECTION
%----------------------------------------------------------------------------------------

\section{References}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cventry{}{Aslan Kasimov (a.kasimov@skoltech.ru)}{}{}{}{}
\cvline{}{Associate Professor in Center for Design, Manufacturing and Materials at Skoltech, Moscow, Russia}

\cventry{}{David Keyes (david.keyes@kaust.edu.sa)}{}{}{}{}
\cvline{}{Professor in Applied Mathematics and Computational Science; Director of Extreme Computing Research Center at KAUST}

\cventry{}{Athanasios Tzavaras (athanasios.tzavaras@kaust.edu.sa)}{}{}{}{}
\cvline{}{Professor, Head of Applied Mathematics and Computational Science at KAUST}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Work Experience}

\cventry{2018--present}{Software developer}{One Omega Seismics}{Thuwal, Saudi Arabia}{}{}
\cventry{2010--2012}{Software developer}{Fabrikant.ru}{Moscow, Russia}{}{}
\cventry{2008--2009}{Part-time software developer}{AWAX Studio}{Moscow, Russia}{}{}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvitem{}{Playing classical and modern music (piano and guitar), sports, history}
%\cvitem{}{Sports (voleyball and bootcamp)}
%\cvitem{}{Contemporary ballet}
%\cvitem{}{History of Ancient Rome and Russia}



\end{document}
